Housing Market Institutions Drive Race and Ethnicity Differences in Energy Consumption

### 2015-03-18 ConferencePaper/DraftEdwardsWoods.Rnw
Added multicore.  Running now

#Either load or create bootstrap estimates
library(boot)
if(file.exists("System.RData")) load("System.RData") else {
 System<-boot(SubsetRECS,BootThing,400)
 save(System,"System.RData")
}
@

>>>>

#Either load or create bootstrap estimates
library(boot)
if(file.exists("System.RData")) load("System.RData") else {
 System<-boot(SubsetRECS,BootThing,400,parallel="multicore",ncpus=4)
 save(System,"System.RData")
}
@
